Miscellaneous Notes on GNU/Hurd

### 2019-06-03 doc/rpctrace.tex
some old changes to 'rpctrace.tex' that I don't remember much about

\task {rpctrace}{}{lr}{}

\task [right = of rpctrace] {Traced Task 2}{}{sl}{}
\task [above = of Traced Task 2] {Traced Task 1}{}{sl}{}
\task [below = of Traced Task 2] {Traced Task 3}{}{sl}{}

\task [above = of rpctrace] {Unknown Task}{}{sl}{}

\draw [port link] (rpctrace Left Port 0) -- +(-1,0) |- (Unknown Task Port 0);
\draw [port link] (Traced Task 2 Port 0) -- (rpctrace Right Port 0);
\draw [port link] (Traced Task 1 Port 0) -| ($(Traced Task 1 Port 0)!.5!(rpctrace Right Port 5)$) |- (rpctrace Right Port 5);
\draw [port link] (Traced Task 3 Port 0) -| ($(Traced Task 3 Port 0)!.5!(rpctrace Right Port -5)$) |- (rpctrace Right Port -5);

@@

\node (Unknown Task recvright) at (Unknown Task Port 0) [recv, anchor=west] {R};

@@

@@

>>>>

\useasboundingbox (-6,-5) rectangle (6.5,5.5);
\scope[transform canvas={scale=0.8}]

\task {rpctrace}{}{blr}{}

\task [above right = of rpctrace.north east] {Traced Task 1}{}{sl}{}
\task [below = of Traced Task 1] {Traced Task 2}{}{sl}{}
\task [below = of Traced Task 2] {Traced Task 3}{}{sl}{}
\task [below = of Traced Task 3] {Traced Task 4}{}{sl}{}

\task [left = of rpctrace] {Unknown Task}{}{r}{
}

\node [message] at (Unknown Task) {};

\draw [port link] (rpctrace Left Port 0) -- (Unknown Task Port 7);
\draw [port link] (Traced Task 1 Port 0) -| ($(Traced Task 1 Port 0)!.6!(rpctrace Right Port 5)$) |- (rpctrace Right Port 5);
\draw [port link] (Traced Task 2 Port 0) -| ($(Traced Task 2 Port 0)!.4!(rpctrace Right Port 0)$) |- (rpctrace Right Port 0);
\draw [port link] (Traced Task 3 Port 0) -| ($(Traced Task 3 Port 0)!.5!(rpctrace Right Port -5)$) |- (rpctrace Right Port -5);

@@

\node (Task 4 recvright) at (Traced Task 4 Port 0) [recv, anchor=west] {R};

\node (Unknown Task recvright) at (Unknown Task Port 7) [recv, anchor=east] {R};
\node (Unknown Task sendright) at (Unknown Task Port -6) [send, anchor=east] {S};

@@

\node (S4) at (rpctrace Right Port -16) [send, anchor=east] {S};
\node (R4) at (rpctrace Left Port -16) [recv, anchor=west] {R};

\draw [port link] (Unknown Task sendright.east) -| ($(Unknown Task sendright.east)!.5!(R4.west)$) |- (R4.west);
\draw [internal link] (R4) -- (S4);

\draw [port link] (S4) -- (Task 4 recvright);

@@

\node (rpctrace message) [message] at ($(R4)!.5!(S4)$) {};

\node (rpctrace message recvright) [recv] at (rpctrace message) {R};

\endscope
\end{tikzpicture}
\end{frame}
